Towards Correct Legion

### 2017-08-26 correctnesshpc/paper.tex

The theorems we are using are described in Figure~\ref{soundnesstheorem} and
Figure~\ref{preservationtheorem} (see \texttt{https://github.com/lanl/formallegion}
for Coq versions of the proofs).

@@

\begin{figure}
\begin{BVerbatim}
Theorem soundness : ∀ e t M H C T1 T2 L S,
  typing [] [] [] e T1  →
  (∃ E v,
    is_value v →
    eval M L H S C e v E).
\end{BVerbatim}
\caption{Soundness theorem}
\label{soundnesstheorem}
\end{figure}

>>>>

The theorems we are using are described in Figure~\ref{preservationtheorem} and
Figure~\ref{soundnesstheorem} (see \texttt{https://github.com/lanl/formallegion}
for Coq versions of the proofs).

@@

\begin{figure}
\begin{BVerbatim}
Theorem Soundness : ∀ e t M H C T1 T2 L S,
  typing [] [] [] e T1  →
  (∃ E v,
    is_value v →
    eval M L H S C e v E).
\end{BVerbatim}
\caption{Soundness theorem}
\label{soundnesstheorem}
\end{figure}
